Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-04-12 thesis_chapter_3.Rmd
small corrections...

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=5, fig.cap="Figure 2: Comparison of mean trajectories. Panel (A) represents hydrodynamic drag only simulations and Panel (B) represents simulations for both wind and hydrodynamic drag, for January, Panel (C) represents hydrodynamic drag only simulations and Panel (D) represents simulations for both wind and hydrodynamic drag, for April. Panel (E) represents hydrodynamic drag only simulations and Panel (F) represents simulations for both wind and hydrodynamic drag, for July. Panel (G) represents hydrodynamic drag only simulations and Panel (H) represents simulations for both wind and hydrodynamic drag, for October. In all panels the passive simulations are represented by black lines."}

@@

Across all simulations particles flowed in a north-westward direction (Figure 3). The density plots for simulations that considered any form of drag showed a higher density of particles along the mean trajectory path compared to the passive simulation which has an almost even density of particles across grids. In addition the density plots show that the particles in simulations that considered any form of drag got entrained in a vorticity while particles in the passive simulation deflected away (Figure 3). Comparison of cross-sectional areas and different drag exposure scenarios show no differences in mean trajectory and spatial patterns in density, with only slight variations across types.

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=5, fig.cap="Figure 3: Comparison of mean trajectories. Panel (A) represents hydrodynamic drag only simulations and Panel (B) represents simulations for both wind and hydrodynamic drag, for January, Panel (C) represents hydrodynamic drag only simulations and Panel (D) represents simulations for both wind and hydrodynamic drag, for April. Panel (E) represents hydrodynamic drag only simulations and Panel (F) represents simulations for both wind and hydrodynamic drag, for July. Panel (G) represents hydrodynamic drag only simulations and Panel (H) represents simulations for both wind and hydrodynamic drag, for October. In all panels the passive simulations are represented by black lines."}

@@

Across all simulations particles flowed in a north-westward direction. The density plots for simulations that considered any form of drag showed a higher density of particles along the mean trajectory path compared to the passive simulation which has an almost even density of particles across grids. In addition the density plots show that the particles in simulations that considered any form of drag got entrained in a vorticity while particles in the passive simulation deflected away (Figure 3). Comparison of cross-sectional areas and different drag exposure scenarios show no differences in mean trajectory and spatial patterns in density, with only slight variations across types.
